Monte Carlo comparisons \\ VBSCAN Cost Action

### 2017-10-18 Setup/report.tex
Update histogram definitions with my suggestions

\newcommand{\eq}[1]{\begin{equation} #1 \end{equation}}
\newcommand{\eqa}[1]{\begin{eqnarray} #1 \end{eqnarray}}
\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}

@@

\section{Observables}
- Cross section within cuts. \\
- Distribution in the number of jets. \\
- Invariant mass of the two hardest jets (two tagged jets). \\
$[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
- \MP{$\ptsub{\Pj_1,\Pj_2,\Pj_3}$ and $y_{\Pj_1,\Pj_2,\Pj_3}$ of the two tagged jets and also the third jet at NLO} (not their sum) \\
$\ptsub{\Pj_1,\Pj_2}$: $[0; 1\TeV]$ with bins of size $25\GeV$ (40 bins). \\
\MP{$\ptsub{\Pj_3}$: $[0; 1\TeV]$ with bins of size $10\GeV$ (100 bins).} \\
\MP{$y_{\Pj_1,\Pj_2,\Pj_3}$: $[-5;5]$ with bins of size $0.5$ (20 bins).} \\
- Invariant mass of the two charged leptons. \\
$[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
- Zeppenfeld variable for $\mu^+$ and $\Pe^+$: \\
$z^*_\ell = |y_\ell - \left(y_{\Pj_1}+y_{\Pj_2} \right)/2|/|\Delta y_{\Pj\Pj}|$ \\
$[0;1.5]$ with bins of size $0.05$ (30 bins). \\
- $|\Delta y_{\Pj \Pj}|$: $[-5;5]$ with bins of size $0.5$ (20 bins).

>>>>

\newcommand{\eq}[1]{\begin{equation} #1 \end{equation}}
\newcommand{\eqa}[1]{\begin{eqnarray} #1 \end{eqnarray}}
\newcommand{\MP}[1]{{ {\color{blue}{ [MP: #1]}} }}
\newcommand{\MR}[1]{{ {\color{blue}{ [MR: #1]}} }}

@@

\section{Observables}
- Cross section within cuts. \\
- Distribution in the number of jets. \\
- Invariant mass of the two hardest jets (two tagged jets). \\
$[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
- \MP{$\ptsub{\Pj_1,\Pj_2,\Pj_3}$ and $y_{\Pj_1,\Pj_2,\Pj_3}$ of the two tagged jets and also the third jet at NLO} (not their sum) \\
$\ptsub{\Pj_1,\Pj_2}$: $[0; 1\TeV]$ with bins of size $25\GeV$ (40 bins). \\
\MP{$\ptsub{\Pj_3}$: $[0; 1\TeV]$ with bins of size $10\GeV$ (100 bins).} \\
\MP{$y_{\Pj_1,\Pj_2,\Pj_3}$: $[-5;5]$ with bins of size $0.5$ (20 bins).} \\
- Invariant mass of the two charged leptons. \\
$[0; 4\TeV]$ with bins of size $100\GeV$ (40 bins). \\
- Zeppenfeld variable for $\mu^+$, $\Pe^+$ \MR{and $\Pj_3$}: \\
$z^*_x = |y_x - \left(y_{\Pj_1}+y_{\Pj_2} \right)/2|/|\Delta y_{\Pj\Pj}|$ \\
$[0;1.5]$ with bins of size $0.05$ (30 bins). \\
- $|\Delta y_{\Pj \Pj}|$: \MR{$[0;10]$} with bins of size $0.5$ (20 bins).
